---
title: "house price index"
author: "Halil İbrahim Türkmen"
date: '2024-04-05'
output: html_document
---

**1.HOUSE PRICES**
In this section, I tried to explain the variations in the house price data using as predictors: Furniture and Decoration expenditures, Building Materials, Hardware, and Ironmongery expenditures, USD/TL exchange rate,Survey Results on Suitability for Purchasing Durable Goods in the Current Period, on a Scale of 100.  From January 2012 to January 2024 monthly data is analysed.
```{r}
require(openxlsx) #library(openxlsx)
require(ggplot2)
require(data.table)
require(skimr)
require(GGally)
require(ggcorrplot)
require(forecast)

options(repr.plot.width=12.7, repr.plot.height=8.5)


data_path='/Users/halilibrahimturkmen/Downloads/EVDS-7.xlsx'


house_prices=read.xlsx(data_path,sheet='EVDS')
str(house_prices)
```
```{r}
ggpairs(house_prices)

```
```{r}
l_fit = lm(TP.HKFE01~.,data=house_prices)
l_fit
```
```{r}
summary(l_fit)

```
```{r}
plot(l_fit)

```

```{r}
l_fit_dropped <- lm(TP.HKFE01 ~ . - TP.KKHARTUT.KT17, data = house_prices)
summary(l_fit_dropped)
```

```{r}
# Create the interaction term using TP.DK.USD.A.YTL
house_prices$interaction <- house_prices$TP.DK.USD.A.YTL * house_prices$TP.KKHARTUT.KT23

# Fit the nonlinear regression model with the interaction term
l_fit_nonlinear_interaction <- lm(TP.HKFE01 ~ .-TP.KKHARTUT.KT23 - TP.KKHARTUT.KT17 -TP.DK.USD.A.YTL  + interaction , data = house_prices)

# Display summary of the model
summary(l_fit_nonlinear_interaction)
```
**2. FEDERAL RESERVE**
I tried to explain the variations in the federal reserve data using as predictors: unemployment rate, USD/TL exchange rate, money supply, TÜFE(consumer price index), and government spendings. From January 2014 to January 2024 monthly data is analysed.
```{r}
data_path='/Users/halilibrahimturkmen/Downloads/EVDS-5.xlsx'
reserve=read.xlsx(data_path,sheet='EVDS')
str(reserve)
```
```{r}
summary_data=skim(reserve)
print(summary_data)
```
```{r}
ggplot(reserve, aes(x=TP.REZVARPD.K1)) + geom_histogram()
```
```{r}
correl_info=cor(reserve)

ggcorrplot(correl_info, 
           hc.order = TRUE, 
           type = "lower",
           lab = TRUE)
```
```{r}
ggpairs(reserve)

```
```{r}
l_fit = lm(TP.REZVARPD.K1~.,data=reserve)
l_fit
```
```{r}
summary(l_fit)
```

**3.ELECTRICITY CONSUMPTION**
I tried to explain the variations in the electricity consumption data using as predictors: BIST 100 index, commercial loans, Manufacturing Industry Capacity Utilization Rate, and number of produced vehicles. From January 2016 to February 2024 monthly data is analysed.

```{r}
data_path='/Users/halilibrahimturkmen/Downloads/EVDS-9.xlsx'
electricity_consumption=read.xlsx(data_path,sheet='EVDS')
str(electricity_consumption)
```
```{r}
ggpairs(electricity_consumption)
```
```{r}
l_fit = lm(TP.ELEKTUKETIM.TKT1~.,data=electricity_consumption)
l_fit
```
```{r}
summary(l_fit)
```
```{r}
plot(l_fit)
```











